Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2019-04-25 paper/paper_JVI_orig_submission.tex
made file with original submission for track changes diffs

\section{Acknowledgments}
We thank Cole Trapnell, Jason Underwood, Robert Bradley, Daniel Stetson, Katherine Xue, and Hannah Itell for helpful suggestions.
We thank Andy Marty and the Fred Hutch Genomics Core for performing the deep sequencing.
This work was supported by the NIAID of the NIH under grant R01 AI127893 and a Burroughs Wellcome Fund Young Investigator in the Pathogenesis of Infectious Diseases grant to JDB.
ABR was supported by a postdoctoral fellowship from the Damon Runyon Cancer Research Foundation (DRG-2227-15).
JRK was supported by a Washington Research Foundation Undergraduate Research Fellowship and a Mary Gates undergraduate research scholarship from the University of Washington.
AtV was supported by joint Wellcome Trust and Royal Society grant 206579/Z/17/Z and Isaac Newton Trust grant 17.37(r).
EE was supported by a Vice-Chancellor’s scholarship from the University of Cambridge.
JDB is an Investigator of the Howard Hughes Medical Institute.
The funders had no role in study design, data collection and interpretation, or the decision to submit the work for publication.

@@

\begin{suppfile}
\caption{
Sequences of the IFN reporters in \FIG{IFNrare}A.
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/IFN_stochastic/IFN_reporter/plasmids}.
}
\label{suppfile:reporter_sequences}
\end{suppfile}

\begin{suppfile}
\caption{
Genbank files giving sequences of the wild-type and synonymously barcoded viruses.
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn.gb} and \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn-double-syn.gb}.
}
\label{suppfile:virus_seqs}
\end{suppfile}

\begin{suppfile}
\caption{
A text file giving the primers used to amplify the influenza cDNAs for PacBio sequencing.
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/WorkflowSchematic/PacBio_primer_list.txt} 
}
\label{suppfile:primer_sequences}
\end{suppfile}

\begin{suppfile}
\caption{
A CSV file giving the genotypes in \FIG{genotypes}.
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/paper/figures/single_cell_figures/genotypes.csv}.
}
\label{suppfile:genotypes}
\end{suppfile}

\begin{suppfile}
\caption{
A CSV file giving the viral mutations and related information in \FIG{mutations}.
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/paper/figures/single_cell_figures/mutations.csv}.
}
\label{suppfile:mutations}
\end{suppfile}

\begin{suppfile}
\caption{
Genbank plasmid maps for the mutant genes cloned into the pHW* bi-directional reverse genetics plasmid~\cite{hoffmann2000dna}.
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/FluVariantPlasmidMaps}
}
\label{suppfile:validation_sequences}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:pacbio_analysis}
HTML rendering of Jupyter notebook that analyzes the PacBio data.
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/raw/master/paper/figures/pacbio_single_cell_figures/pacbio_analysis.html}.
The actual Jupyter notebook is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/pacbio_analysis.ipynb}.
}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:monocle_analysis}
HTML rendering of Jupyter notebook that analyzes the annotated cell-gene matrix.
%See \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/raw/master/paper/figures/single_cell_figures/monocle_analysis.html}.
The actual Jupyter notebook is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/monocle_analysis.ipynb}.
}
\end{suppfile}

>>>>

\section{Acknowledgments}
We thank Cole Trapnell, Jason Underwood, Robert Bradley, Daniel Stetson, Katherine Xue, and Hannah Itell for helpful suggestions.
We thank Andy Marty and the Fred Hutch Genomics Core for performing the deep sequencing.
This work was supported by the NIAID of the NIH under grant R01 AI127893 and a Burroughs Wellcome Fund Young Investigator in the Pathogenesis of Infectious Diseases grant to JDB.
ABR was supported by a postdoctoral fellowship from the Damon Runyon Cancer Research Foundation (DRG-2227-15).
JRK was supported by a Washington Research Foundation Undergraduate Research Fellowship and a Mary Gates undergraduate research scholarship from the University of Washington.
AtV was supported by joint Wellcome Trust and Royal Society grant 206579/Z/17/Z and Isaac Newton Trust grant 17.37(r).
EE was supported by a Vice-Chancellor's scholarship from the University of Cambridge.
JDB is an Investigator of the Howard Hughes Medical Institute.
The funders had no role in study design, data collection and interpretation, or the decision to submit the work for publication.

@@

\begin{suppfile}
\caption{
Sequences of the IFN reporters in \FIG{IFNrare}A are at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/IFN_stochastic/IFN_reporter/plasmids}.
}
\label{suppfile:reporter_sequences}
\end{suppfile}

\begin{suppfile}
\caption{
Genbank files giving sequences of the wild-type and synonymously barcoded viruses are at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn.gb} and \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/data/flu_sequences/flu-wsn-double-syn.gb}.
}
\label{suppfile:virus_seqs}
\end{suppfile}

\begin{suppfile}
\caption{
A text file giving the primers used to amplify the influenza cDNAs for PacBio sequencing is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/WorkflowSchematic/PacBio_primer_list.txt} 
}
\label{suppfile:primer_sequences}
\end{suppfile}

\begin{suppfile}
\caption{
A CSV file giving the genotypes in \FIG{genotypes} is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/paper/figures/single_cell_figures/genotypes.csv}.
}
\label{suppfile:genotypes}
\end{suppfile}

\begin{suppfile}
\caption{
A CSV file giving the viral mutations and related information in \FIG{mutations} is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/paper/figures/single_cell_figures/mutations.csv}.
}
\label{suppfile:mutations}
\end{suppfile}

\begin{suppfile}
\caption{
Genbank plasmid maps for the mutant genes cloned into the pHW* bi-directional reverse genetics plasmid~\cite{hoffmann2000dna} are at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/FluVariantPlasmidMaps}.
}
\label{suppfile:validation_sequences}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:pacbio_analysis}
The Jupyter notebook that analyzes the PacBio data is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/pacbio_analysis.ipynb}.
}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:monocle_analysis}
The Jupyter notebook that analyzes the annotated cell-gene matrix is at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/monocle_analysis.ipynb}.
}
\end{suppfile}
